---
runtime: shiny
title: "Deliverable 5.2" 
date: "`r format(Sys.Date(), '%d.%m.%Y')`"
params:
  write_excel: FALSE
  echo: FALSE
  shiny: FALSE
  saveFig: TRUE
  out_dir:
output: 
  html_document:
    css: style.css
    includes:
      in_header: hero-image.html
    keep_md: TRUE
---

```{r, echo=FALSE}
suppressMessages({
  library("climate.campaigneRs")
  library("ggplot2")
  library("scales")
  library("leaflet")
  library("showtext")
  library("dplyr")
  library("kableExtra")
  library("formattable")
  library("DT")
  library("ggmice")
  library("stringr")
  library("openxlsx")
  library("tidyr")
  library("sysfonts")
  library("shiny")
  sysfonts::font_add_google("Poppins", family = "poppins")
})
```


# Introduction
This report was auto generated using the `render_report()` function from the `climate.campaigneRs` R package. The report was generated with various parameters, including `saveFig` which controls whether all plots are saved as PNG, `write_excel` and `out_dir` which control if the API responses are saved as a single Excel file to the specified directory, and `echo` which controls whether the code for this report is shown.
The `shiny` parameter in the `render_report()` indicates if the report will be rendered in a `shiny` format, which allows for interactive filtering of the aggregated challenges by various variables. On the other hand, if `shiny = FALSE` (which is the default value), the report will be rendered in standard HTML format, without the interactive filtering feature.

<br>

The key functions in this package are

- get_\*() where \* is one of data, challenges, user_values, weekly_assignments
  - Access API endpoint
  - Validate and prepare data
  - Return R data frame

- render_report()
  - Get latest data from API with get_\*() functions
  - Optional: save all data in one Excel file
  - Plot and handle missing values
  - User data visualization
  - Overview of optional variables from footprint calculation and missing values
  - Interactive table of all challenges
  - Top 10 challenges
  - Visualization of follow up questions of top 10 challenges
  - HTML or Shiny report



<br>

# Installation

The R package will be made available on GitHub. 

```{r, echo=TRUE, eval=FALSE}
devtools::install_github("TBA/climate.campaigneRs")
```


<br>

# Access the database

Accessing and preparing the data involves these steps:

- Handling empty strings and NA
- Error handling 
- Verifying variables
- Data: Adding variables "challenges.X.success" that indicate if a challenge was finished **successfully**

```{r, echo=TRUE}
user_values <- climate.campaigneRs::get_user_values()
challenges <- climate.campaigneRs::get_challenges()
weekly_assignments <- climate.campaigneRs::get_weekly_assignments()

result <- climate.campaigneRs::get_data(challenges)
data <- result$data
```

```{r, echo=FALSE}
if (params$saveFig) {
  dev = "png"
  dpi = 300
} else {
  dev = NULL
  dpi = NULL
}

knitr::opts_chunk$set(eval = !is.null(data), 
                      echo = params$echo, 
                      fig.align = "center",
                      fig.width = 3, 
                      fig.height = 2,
                      dev = dev,
                      dpi = dpi
                      )

textsize = 6
labelsize = 1.5
```


```{r, results='asis'}
value <- nrow(data)

# info box
cat('<div style="text-align:left; background-color:#69a341; color:#fff; padding:10px; border-radius: 5px; max-width: 325px">')
cat(paste0('<h3>App users (', format(Sys.Date(), '%d.%m.%Y'),  ')</h3>'))
cat('<p>', value, '</p>')
cat('</div>')
```


```{r}
if (params$write_excel) {
  out <- openxlsx::createWorkbook()

  openxlsx::addWorksheet(out, "data")
  openxlsx::addWorksheet(out, "user_values")
  openxlsx::addWorksheet(out, "challenges")
  openxlsx::addWorksheet(out, "weekly_assignments")
  
  openxlsx::writeData(out, sheet = "data", x = data)
  openxlsx::writeData(out, sheet = "user_values", x = user_values)
  openxlsx::writeData(out, sheet = "challenges", x = challenges)
  openxlsx::writeData(out, sheet = "weekly_assignments", x = weekly_assignments)
  
  out_name <- paste0("data_", Sys.Date(), ".xlsx")
  openxlsx::saveWorkbook(out, file.path(params$out_dir, out_name), overwrite = TRUE)

}
```
<br>

# Data validation

## Missing values pattern in `data` dataset

Users that never interacted with the app are removed from the dataset. 
This is the case when all values that require input from users are missing.

```{r NA-pattern, fig.showtext=TRUE, fig.width=6, fig.height=4}
# personal information

from <- "uid"
to <- "occupation"

df <- data[, colnames(data)[which(colnames(data) == from):which(colnames(data) == to)]]
g <- ggmice::plot_pattern(df, rotate = FALSE)
g <- suppressMessages(
  g + theme(text = element_text(size = textsize), 
            axis.title.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0)),
            axis.title.y.right = element_text(margin = margin(t = 0, r = 0, b = 0, l = 5)),
            axis.title.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)),
            axis.title.x.top = element_text(margin = margin(t = 0, r = 0, b = 5, l = 0))) +
    scale_fill_manual(values = c(observed = "#69a341", 
                                 missing = "#3f3f3f"))
  )
g
```



```{r}
# remove users that did not provide any user information
df <- df[rowSums(is.na(subset(df, select = -c(uid)))) != ncol(subset(df, select = -c(uid))), ]
data <- data[data$uid %in% df$uid, ]
```


# User data


```{r Gender-distribution, fig.showtext=TRUE} 
climate.campaigneRs::barchart(data$gender, useNA = FALSE, textsize = textsize,
                              labelsize = labelsize, 
                              title = paste0("Gender distribution \nn = ", 
                                             sum(!is.na(data$gender)), ", NA = ", 
                                             sum(is.na(data$gender))))
```

<br><br><br>


```{r Age-distribution, fig.showtext=TRUE}
climate.campaigneRs::barchart(data$age, useNA = FALSE, textsize = textsize,
                              labelsize = labelsize,
                              title = paste0("Age distribution \nn = ", 
                                             sum(!is.na(data$age)), ", NA = ", 
                                             sum(is.na(data$age))))
```

<br><br><br>



```{r Age-Gender-distribution, fig.showtext=TRUE, fig.height=2.5}
tab <- prop.table(table(data$age, data$gender), margin = 2)
tab <- as.data.frame(tab)
label <- paste0(round(tab$Freq * 100, 1), "%")
label[label == "0%"] <- ""


ggplot(tab, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity", fill = "#69a341") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, max(tab$Freq) * 1.2), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_x_discrete(limits = rev(levels(tab$Var1))) + 
  theme(panel.background = element_rect(fill = NA),
        axis.line = element_line(linetype = "solid"),
        text = element_text(size = textsize, family = "poppins"),
        plot.title = element_text(size = textsize)) +
  geom_text(aes(label = label), hjust = -0.1, size = labelsize,
            family = "poppins") +
  ggtitle(paste0("Age distribution by gender \nn = ", 
                 sum(table(data$age, data$gender)), ", NA = ", 
                 nrow(data) - sum(table(data$age, data$gender)))) +
  ylab("") +
  xlab("") +
  annotate("segment", x = -Inf, xend = Inf, y = -Inf, yend = -Inf) +
  annotate("segment", x = -Inf, xend = -Inf, y = -Inf, yend = Inf) +
  facet_wrap(~Var2) +
  coord_flip()
```

<br><br><br>

```{r Education-distribution, fig.showtext=TRUE}
climate.campaigneRs::barchart(data$education, useNA = FALSE, textsize = textsize,
                              labelsize = labelsize, 
                              title = paste0("Education distribution \nn = ", 
                                             sum(!is.na(data$education)), ", NA = ", 
                                             sum(is.na(data$education))))
```


<br><br><br>


```{r occupation-distribution, fig.showtext=TRUE}
climate.campaigneRs::barchart(data$occupation, useNA = FALSE, textsize = textsize,
                              labelsize = labelsize,
                              title = paste0("Occupation distribution \nn = ", 
                                             sum(!is.na(data$occupation)), ", NA = ", 
                                             sum(is.na(data$occupation))))
```



```{r}
# Dataset from Google Public Data, licensed under CC BY 4.0
# See https://developers.google.com/public-data/docs/canonical/countries_csv for details

countries <- read.csv2("countries.csv", encoding = "latin1")
countries$latitude <- as.numeric(countries$latitude)
countries$longitude <- as.numeric(countries$longitude)

attr(countries, "source") <- "Dataset from Google Public Data, licensed under CC BY 4.0. See https://developers.google.com/public-data/docs/canonical/countries_csv for details."
```



### Number of users by country

```{r}
tab <- table(data$country)
tab <- as.data.frame(tab)

# inner join
tab_merged <- merge(countries, tab, by.x = "name", by.y = "Var1")
```


We want to check whether a country instance from the API is not a valid country name. 
Erroneous observations will be removed from the spatial representation of the data.

```{r}
country_check <- tab_merged$name[!(tab_merged$name %in% unique(data$country))]

if (length(country_check) == 0) {
  print("No invalid countries.")
} else {
  print("The following countries are not valid. Please contact the package authors.")
  print(country_check)
}
```


```{r, fig.showtext=TRUE, out.width = '75%'}
labels <- sprintf("%s: %g users", tab_merged$name, tab_merged$Freq) |>
  lapply(htmltools::HTML)

leaflet::leaflet(tab_merged) |>
  leaflet::addProviderTiles(providers$CartoDB.Positron) |>
  leaflet::addCircleMarkers(lng = ~longitude, lat = ~latitude, 
                   radius = sqrt(tab_merged$Freq) * 3,
                   color = "#69a341",
                   fillOpacity = 0.5,
                   label = labels,
                   labelOptions = leaflet::labelOptions(fontFamily = "Poppins",
                                               textsize = "20px")
                   )
```

<br><br><br>

### User engagement by country
The metric of the ratio of accepted and finished challenges is used to describe the 
level of engagement and completion rates of users over all challenges by countries.

The ratio of accepted and finished challenges is given by $\frac{\text{Number of finished challenges}}{\text{Number of accepted challenges}}$.


```{r, fig.showtext=TRUE, out.width = '75%'}
accepted <- climate.campaigneRs::get_subset(data, "\\.accepted")[,-1]
finished <- climate.campaigneRs::get_subset(data, "\\.finished")[,-1]

accepted <- accepted[,-c(1:7)]
finished <- finished[,-c(1:7)]

accepted[!is.na(accepted)] <- 1
accepted[is.na(accepted)] <- 0

finished[!is.na(finished)] <- 1
finished[is.na(finished)] <- 0

finished <- finished |>
   mutate_all(as.numeric)

accepted <- accepted |>
   mutate_all(as.numeric)


data$finished <- rowSums(finished)
data$accepted <- rowSums(accepted)


data_agg <- aggregate(cbind(finished, accepted) ~ country, data = data, FUN = sum)

data_agg$ratio <- ifelse(data_agg$accepted > 0, data_agg$finished / data_agg$accepted, 0)

tab_merged <- merge(countries, data_agg, by.x = "name", by.y = "country")


labels <- sprintf("%s: %g %%", tab_merged$name, round(tab_merged$ratio * 100, 1)) |>
  lapply(htmltools::HTML)

leaflet::leaflet(tab_merged) |>
  leaflet::addProviderTiles(providers$CartoDB.Positron) |>
  leaflet::addCircleMarkers(lng = ~longitude, lat = ~latitude,
                   radius = sqrt(tab_merged$ratio * 100) * 3,
                   color = "#69a341",
                   fillOpacity = 0.5,
                   label = labels,
                   labelOptions = leaflet::labelOptions(fontFamily = "Poppins",
                                               textsize = "20px")
                   )
```

<br><br><br>

### Overview of optional variables used to calcualte the carbon footprint

```{r, fig.showtext=TRUE}
# nur für Type "select"

from <- "numberOfPortableElectricHeatersKey"
to <- "electricConsumptionForHeatingKey"

vars <- colnames(data)[which(colnames(data) == from):which(colnames(data) == to)]
uv <- user_values[user_values$key %in% vars, ]
uv <- uv[uv$type == "select", ]

vars <- intersect(vars, uv$key)
tabs <- c()

for (i in 1:length(vars)) {
  # factor vars
  cols <- colnames(uv[uv$key == vars[i], ])[grepl("option[0-9]+Label", colnames(uv[uv$key == vars[i], ]))]
  lvls <- unlist(uv[uv$key == vars[i], cols])
  lvls <- lvls[lvls != ""]
  
  data[, vars[i]] <- factor(data[, vars[i]], levels = lvls)
  
  tab <- rbind(table(data[, vars[i]], useNA = "always"),
             (table(data[, vars[i]], useNA = "always") / length(data[, vars[i]])) * 100)
  tab <-  data.frame(tab, check.names = FALSE)

  var <- colnames(tab)
  grp <- rep(user_values[user_values$key == vars[i],]$label, ncol(tab))
  tab <- data.frame(t(tab))
  tab <- cbind(grp, var, tab)
  row.names(tab) <- NULL
  
  tab$X2 <- round(tab$X2, 1)
  tabs <- rbind(tabs, tab)

}

assign_group_rows <- function(x) {
  unique_grps <- unique(tabs$grp)
  
  for (g in 1:length(unique_grps)) {
    starts <- min(which(tabs$grp == unique_grps[g]))
    ends <- max(which(tabs$grp == unique_grps[g]))
    
    x <- kableExtra::group_rows(x, unique_grps[g], starts, ends,
                    label_row_css = paste0("background-color: ", "#69a341",
                                           "; color: #F1F1F1;")
                    )
    }
    x
}

names(tabs)[2] <- " "

tabs |>
  dplyr::mutate(
         n = X1,
         "%" = formattable::color_bar("#69a341")(X2)) |>
  dplyr::select(!c(grp, X1, X2)) |>
  kableExtra::kable("html", escape = FALSE) |>
  kableExtra::kable_styling("hover", full_width = FALSE) |>
  assign_group_rows()
```

<br><br><br>

# Challenges

Challenges are aggregated when the title, category and duration are identical.

The following count variables are available for each challenge: 

- `accepted`: Number of users who accepted the challenge
- `finished`: Number of users who finished the challenge
- `rejected`: Number of users who rejected the challenge; omitted from table
- `success`: Number of users who **successfully** finished the challenge, extracted from `Yes` answers from questions "Were you successful in completing this challenge?"
- `fail`: Number of users who **failed** to finish the challenge, extracted from `No` answers from questions "Were you successful in completing this challenge?"
- `open`: Difference between `accepted` and `finished`
- `diff`: Difference between `finished`, `success` and `fail`

<br>

```{r}
if (params$shiny) { 
  shiny::fluidPage(
    selectInput("gender", label = "Filter gender:",
              choices = levels(data$gender), multiple = TRUE),

    selectInput("age", label = "Filter age:",
                choices = levels(data$age), multiple = TRUE),
  
    selectInput("country", label = "Filter country:",
                choices = sort(unique(data$country)), multiple = TRUE),
  
    selectInput("education", label = "Filter education:",
                choices = levels(data$education), multiple = TRUE),
  
    selectInput("occupation", label = "Filter occupation:",
                choices = levels(data$occupation), multiple = TRUE)
  )
}
```

```{r}
df <- climate.campaigneRs::get_subset(data, "\\.accepted|\\.rejected|\\.finished|\\.success")
```


```{r}
if (params$shiny) {
  df <- data
  df_filtered <- reactive({
  
  if (!is.null(input$gender)) {
    df <- subset(df, gender %in% input$gender)
  }
  if (!is.null(input$age)) {
    df <- subset(df, age %in% input$age)
  }
  if (!is.null(input$country)) {
    df <- subset(df, country %in% input$country)
  }
  if (!is.null(input$education)) {
    df <- subset(df, education %in% input$education)
  }
  if (!is.null(input$occupation)) {
    df <- subset(df, occupation %in% input$occupation)
  }
    climate.campaigneRs::aggregate_challenges(df, challenges)
  })
}


```


```{r, fig.showtext=TRUE}
if (params$shiny) {
  filtered_table <- DT::renderDataTable({
  DT::datatable(df_filtered(),
          extensions = "Buttons",
          options = list(dom = "Blfrtip",
                         buttons = c("copy", "csv", "excel", "pdf")
                         ),
          filter = list(position = "top", clear = TRUE),
          selection = "multiple",
          rownames = FALSE,
          escape = FALSE
          )
    })
  filtered_table
} else {
  DT::datatable(aggregate_challenges(data, challenges),
                extensions = "Buttons",
                options = list(dom = "Blfrtip",
                               buttons = c("copy", "csv", "excel", "pdf")
                               ),
                filter = list(position = "top", clear = TRUE),
                selection = "multiple",
                rownames = FALSE,
                escape = FALSE
                )
}

```

<br><br><br>

## Top 10 challenges according to successful completions


```{r Top10-challenges, fig.showtext=TRUE}
# TOP 10 challenges and find interesting questions
challenges_df <- aggregate_challenges(data, challenges)

top10 <- challenges_df[with(challenges_df, order(-success)),][1:10,]
top10$title <- factor(top10$title, levels = top10$title[order(top10$success)])


ggplot(top10, aes(x = title, y = success)) +
  geom_bar(stat = "identity", fill = "#69a341") +
  scale_y_continuous(limits = c(0, max(top10$success) * 1.1)) +
  scale_x_discrete(limits = levels(top10$title), labels = function(x) stringr::str_wrap(x, width = 25)) + 
  ylab("Number of successful completions") +
  xlab("") +
  theme_classic() +
  geom_text(aes(label = success), hjust = -0.1, size = labelsize) +
  theme(text = element_text(size = textsize - 1, family = "poppins"),
        plot.title = element_text(size = textsize, vjust = 3)) +
  coord_flip()
``` 

<br><br><br>

<!-- ### Cumulative sum of successful completions -->

```{r Top10_successful-completions, fig.showtext=TRUE, fig.width=3.5, fig.height=2.5, eval=FALSE}
if (!params$shiny) {
  finished <- climate.campaigneRs::get_subset(data, "\\.finished")[,-c(2:7)]
  success <- climate.campaigneRs::get_subset(data, "\\.success")[, -c(2:7)]
  
  finished_long <- finished |>
    tidyr::pivot_longer(-uid)
  
  finished_long$challenge <- gsub("challenges\\.", "", finished_long$name)
  finished_long$challenge <- gsub("\\..*", "", finished_long$challenge)
  finished_long <- subset(finished_long, select = -name)
  
  success_long <- success |>
    tidyr::pivot_longer(-uid)
  
  success_long$challenge <- gsub("challenges\\.", "", success_long$name)
  success_long$challenge <- gsub("\\..*", "", success_long$challenge)
  success_long <- subset(success_long, select = -name)
  
  df <- merge(finished_long, success_long, by = c("uid", "challenge"))
  
  df <- df[df$value.y %in% "Yes", ]
  
  df <- na.omit(df)
  df$value.y[df$value.y == "Yes"] <- 1
  df$value.y <- as.numeric(df$value.y)
  df$value.x <- as.Date(df$value.x)
  
  df <- df[df$challenge %in% challenges[challenges$title %in% top10$title, "id"], ]
  df <- aggregate(df$value.y, by = list(df$value.x, df$challenge), FUN = sum)
  
  df_cumsum <- df |>
    group_by(Group.2) |>
    arrange(Group.1) |>
    mutate(cs = cumsum(x)) |>
    ungroup()
  
  df_cumsum <- merge(df_cumsum, challenges[challenges$id %in% df_cumsum$Group.2, 1:2], by.x = "Group.2", by.y = "id")
  df_cumsum$title <- factor(df_cumsum$title, levels = top10$title)
  
  str_wrap_factor <- function(x, ...) {
    levels(x) <- str_wrap(levels(x), ...)
    x
  }
  
  df_cumsum |>
    ggplot(aes(x = Group.1, y = cs, group = title, color = str_wrap_factor(title, 20))) +
    geom_line() +
    scale_x_date(date_labels = "%d.%m.%Y", date_breaks = "2 weeks") +
    theme_classic() +
    xlab("") +
    ylab("") +
    theme(text = element_text(size = textsize - 2, family = "poppins"),
          plot.title = element_text(size = textsize - 2, vjust = 3),
          axis.text.x = element_text(angle = 90, vjust = 0.5),
          legend.title = element_blank())
}


```


<br><br><br>

## Follow up questions to the top 10 challenges
For each of the top 10 challenges a follow up question is selected manually.
The structure of follow up questions varies between questions. 
This section needs to be updated by hand if the top 10 challenges change.
Setting `echo = TRUE` in `render_report()`shows a sample that identifies a follow up
question.

```{r, eval=FALSE}
# Example for identify interesting follow up question for challenge
# "Don't use your car for the next 24 hours"
c <- challenges[challenges$title %in% "Don't use your car for the next 24 hours", ]
View(c)

c$questions.3.question
key <- c$questions.3.userValueId # this is the key that is used to extract the values in "data"
data[, key]
```

<br>

### 1. Don't use your car for the next 24 hours
##### What did you use instead of your personal vehicle?
```{r Top10_1_mobility_001_success_2, fig.showtext=TRUE}
tab <- table(data$mobility_001_success_2)
tab <- as.data.frame(tab)
tab$Var1 <- factor(tab$Var1, levels = tab$Var1[order(tab$Freq)])

ggplot(tab, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity", fill = "#69a341") +
  scale_y_continuous(limits = c(0, max(tab$Freq) * 1.1)) +
  ylab("Number of successful completions") +
  xlab("") +
  theme_classic() +
  geom_text(aes(label = Freq), hjust = -0.1, size = labelsize) +
  theme(text = element_text(size = textsize, family = "poppins"),
        plot.title = element_text(size = textsize, vjust = 3)) +
  coord_flip()
```

<br><br><br>

### 2. Active transport only - tomorrow!
##### Which active travel mode of transport did you choose?
```{r Top10_2_mobility_002_success_2, fig.showtext=TRUE}

tab <- table(data$mobility_002_success_2)
tab <- as.data.frame(tab)
tab$Var1 <- factor(tab$Var1, levels = tab$Var1[order(tab$Freq)])

ggplot(tab, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity", fill = "#69a341") +
  scale_y_continuous(limits = c(0, max(tab$Freq) * 1.1)) +
  scale_x_discrete(limits = levels(tab$Var1), labels = function(x) stringr::str_wrap(x, width = 25)) + 
  ylab("Number of successful completions") +
  xlab("") +
  theme_classic() +
  geom_text(aes(label = Freq), hjust = -0.1, size = labelsize) +
  theme(text = element_text(size = textsize, family = "poppins"),
        plot.title = element_text(size = textsize, vjust = 3)) +
  coord_flip()
```

<br><br><br>

### 3. Set your dishwasher to eco mode
##### How many times a week do you usually use your dishwasher?
```{r Top10_3_dishwasher_to_eco_mode_challenge_start_1, fig.showtext=TRUE}
tab <- table(data$`dishwasher to eco mode challenge start 1`)
tab <- as.data.frame(tab)

bins <- c(1, 3, 6, 9, 20)

tab$Var1 <- as.numeric(as.character(tab$Var1))
tab$bin <- cut(tab$Var1, breaks = bins, labels = c("1-3 times per week", "4-6 times per week", 
                                                   "7-9 times per week", "10-20 times per week"), 
               include.lowest = TRUE)

tab <- aggregate(tab$Freq, by = list(tab$bin), FUN = sum)
names(tab) <- c("Var1", "Freq")

ggplot(tab, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity", fill = "#69a341") +
  scale_y_continuous(limits = c(0, max(tab$Freq) * 1.1)) +
  scale_x_discrete(limits = rev(levels(tab$Var1)), labels = function(x) stringr::str_wrap(x, width = 25)) + 
  ylab("Number of successful completions") +
  xlab("") +
  theme_classic() +
  geom_text(aes(label = Freq), hjust = -0.1, size = labelsize) +
  theme(text = element_text(size = textsize, family = "poppins"),
        plot.title = element_text(size = textsize, vjust = 3)) +
  coord_flip()
```

<br><br><br>

### 4. Spare your laundry from the dryer for 1 week
##### How many times a week do you usually use a tumble dryer?
```{r Top10_4_dryerUsesPerWeek, fig.showtext=TRUE}
tab <- table(data$dryerUsesPerWeek)
tab <- as.data.frame(tab)

bins <- c(-1, 0, 2, 5, 8)

tab$Var1 <- as.numeric(as.character(tab$Var1))
tab$bin <- cut(tab$Var1, breaks = bins, labels = c("0 times per week", "1-2 times per week", 
                                                   "3-5 times per week", "6-8 times per week"), 
               include.lowest = TRUE)

tab <- aggregate(tab$Freq, by = list(tab$bin), FUN = sum)
names(tab) <- c("Var1", "Freq")

ggplot(tab, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity", fill = "#69a341") +
  scale_y_continuous(limits = c(0, max(tab$Freq) * 1.1)) +
  scale_x_discrete(limits = rev(levels(tab$Var1)), labels = function(x) stringr::str_wrap(x, width = 25)) + 
  ylab("Number of successful completions") +
  xlab("") +
  theme_classic() +
  geom_text(aes(label = Freq), hjust = -0.1, size = labelsize) +
  theme(text = element_text(size = textsize, family = "poppins"),
        plot.title = element_text(size = textsize, vjust = 3)) +
  coord_flip()

```

<br><br><br>

### 5. Make today a no meat day
##### What did you eat instead of meat products?
```{r Top10_5_diet_003_success_2, fig.showtext=TRUE}

tab <- table(data$diet_003_success_2)
tab <- as.data.frame(tab)
tab$Var1 <- factor(tab$Var1, levels = tab$Var1[order(tab$Freq)])

ggplot(tab, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity", fill = "#69a341") +
  scale_y_continuous(limits = c(0, max(tab$Freq) * 1.1)) +
  scale_x_discrete(limits = levels(tab$Var1), labels = function(x) stringr::str_wrap(x, width = 25)) + 
  ylab("Number of successful completions") +
  xlab("") +
  theme_classic() +
  geom_text(aes(label = Freq), hjust = -0.1, size = labelsize) +
  theme(text = element_text(size = textsize, family = "poppins"),
        plot.title = element_text(size = textsize, vjust = 3)) +
  coord_flip()

```

<br><br><br>

### 6. Shower with a stopwatch next week
##### How long are your showers normally (in minutes)?
```{r Top10_6_shower_duration, fig.showtext=TRUE}

tab <- table(data$`shower duration`)
tab <- as.data.frame(tab)

bins <- c(0, 4, 10, 15, Inf)

tab$Var1 <- as.numeric(as.character(tab$Var1))
tab$bin <- cut(tab$Var1, breaks = bins, labels = c("less than 5 mins", "5-10 mins", 
                                                   "11-15 mins", "more than 15mins"), 
               include.lowest = TRUE)

tab <- aggregate(tab$Freq, by = list(tab$bin), FUN = sum)
names(tab) <- c("Var1", "Freq")

ggplot(tab, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity", fill = "#69a341") +
  scale_y_continuous(limits = c(0, max(tab$Freq) * 1.1)) +
  scale_x_discrete(limits = rev(levels(tab$Var1)), labels = function(x) stringr::str_wrap(x, width = 25)) + 
  ylab("Number of successful completions") +
  xlab("") +
  theme_classic() +
  geom_text(aes(label = Freq), hjust = -0.1, size = labelsize) +
  theme(text = element_text(size = textsize, family = "poppins"),
        plot.title = element_text(size = textsize, vjust = 3)) +
  coord_flip()


```

<br><br><br>

### 7. Unplug unused electrical appliances for two weeks
##### Please select the most relevant option that led to your success with this challenge: 
```{r Top10_7_energy_002_success_2, fig.showtext=TRUE}

tab <- table(data$energy_002_success_2)
tab <- as.data.frame(tab)
tab$Var1 <- factor(tab$Var1, levels = tab$Var1[order(tab$Freq)])

ggplot(tab, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity", fill = "#69a341") +
  scale_y_continuous(limits = c(0, max(tab$Freq) * 1.1)) +
  scale_x_discrete(limits = levels(tab$Var1), labels = function(x) stringr::str_wrap(x, width = 25)) + 
  ylab("Number of successful completions") +
  xlab("") +
  theme_classic() +
  geom_text(aes(label = Freq), hjust = -0.1, size = labelsize) +
  theme(text = element_text(size = textsize, family = "poppins"),
        plot.title = element_text(size = textsize, vjust = 3)) +
  coord_flip()
```

<br><br><br>

### 8. Recycle some rubbish
##### Do you already dispose of all of your recycable rubbish correctly?
```{r Top10_8_waste_002_success_2, fig.showtext=TRUE}

tab <- table(data$waste_002_success_2)
tab <- as.data.frame(tab)
tab$Var1 <- factor(tab$Var1, levels = tab$Var1[order(tab$Freq)])

ggplot(tab, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity", fill = "#69a341", width = 0.6) +
  scale_y_continuous(limits = c(0, max(tab$Freq) * 1.1)) +
  scale_x_discrete(limits = levels(tab$Var1), labels = function(x) stringr::str_wrap(x, width = 25)) + 
  ylab("Number of successful completions") +
  xlab("") +
  theme_classic() +
  geom_text(aes(label = Freq), hjust = -0.1, size = labelsize) +
  theme(text = element_text(size = textsize, family = "poppins"),
        plot.title = element_text(size = textsize, vjust = 3)) +
  coord_flip()
```

<br><br><br>

### 9. Try something fun that doesn‘t require electricity
##### Please select the most relevant option that led to your success with this challenge: 
```{r Top10_9_energy_008_success_2, fig.showtext=TRUE}

tab <- table(data$energy_008_success_2)
tab <- as.data.frame(tab)
tab$Var1 <- factor(tab$Var1, levels = tab$Var1[order(tab$Freq)])

ggplot(tab, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity", fill = "#69a341") +
  scale_y_continuous(limits = c(0, max(tab$Freq) * 1.1)) +
  scale_x_discrete(limits = levels(tab$Var1), labels = function(x) stringr::str_wrap(x, width = 25)) + 
  ylab("Number of successful completions") +
  xlab("") +
  theme_classic() +
  geom_text(aes(label = Freq), hjust = -0.1, size = labelsize) +
  theme(text = element_text(size = textsize, family = "poppins"),
        plot.title = element_text(size = textsize, vjust = 3)) +
  coord_flip()
```


<br><br><br>

### 10. Set your washing machine to eco mode
##### Please select the most relevant option that led to your success with this challenge: 
```{r Top10_10_energy_006_success_2, fig.showtext=TRUE}
# No response to: How many times a week do you usually use your washing machine?
tab <- table(data$energy_006_success_2)
tab <- as.data.frame(tab)
tab$Var1 <- factor(tab$Var1, levels = tab$Var1[order(tab$Freq)])

ggplot(tab, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity", fill = "#69a341") +
  scale_y_continuous(limits = c(0, max(tab$Freq) * 1.1)) +
  scale_x_discrete(limits = levels(tab$Var1), labels = function(x) stringr::str_wrap(x, width = 25)) + 
  ylab("Number of successful completions") +
  xlab("") +
  theme_classic() +
  geom_text(aes(label = Freq), hjust = -0.1, size = labelsize) +
  theme(text = element_text(size = textsize, family = "poppins"),
        plot.title = element_text(size = textsize, vjust = 3)) +
  coord_flip()
```


